### 2022-09-28 Thesis/text/einleitung.tex
.

This thesis explores possibilities for improving current systems by adding a dedicated behavior planning component. Furthermore, the thesis provides an implementation of exemplary behaviors and provide a system architecture to incorporate behavior planning in other robots, too.

The desired outcomes of this implemented software is an increase in robustness and a decrease in required human actions during several scenarios. In these scenarios, failures and problems are artificially induced to test the robot's abilities to behave autonomously.

>>>>

This thesis will explore possibilities for improving current systems by adding a dedicated behavior planning component. Furthermore, the thesis seeks to provide an implementation of exemplary behaviors and a system architecture to incorporate behavior planning in other robots, too.

The desired outcomes of this implemented software will be an increase in robustness and a decrease in required human actions during several scenarios. In these scenarios, failures and problems will be artificially induced to test the robot's abilities to behave autonomously.
